The Globular Cluster System of the Auriga Simulations

### 2019-04-26 AurigaGCS.tex
Some sentences on GC formation, and some sentences on FeH distribution

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer a unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies. In theory, this information 
should be readily available and easily observable in the low redshift Universe, given 
that GCs survive nearly a Hubble time of evolution within the violent galactic 
environments they live in. However, a prerequisite to infer galactic histories
from observations of GC systems is to understand the subtleties of the GC formation
and evolution itself.

Several formation scenerarios are consistent with the observations of globular 
cluster populations. One important constraint comes from bimodality in the 
colour distribution, which is indicative of a bimodality in the underlying 
metallicity distribution of GC systems. For example, GCs in the MW are typically
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo
\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities
between the spatial distribution and chemical signature of the `blue' GCs show
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative
age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger
than the metal-rich counterpart \citep{2005AJ....130..116D}.

\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
formation. The authors argue that the observed metal-rich and metal-poor

In a recent study Chiou et al. speculate that GCs may form in supersonically
induced gasseous objects at high redshifts. These objects are free of dark matter 
and populate a mass range consistent with the typical mass scale of GCs. 
Interestingly, the authors find present-day absolute visual magnitude and 
characteristic scales consistent with GCs in the Local group, based on a 
rudimentary star formation model.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the MW GCS age distribution (Figure~\ref{fig:MW-M31-age}),
and following \citet{2017MNRAS.465.3622R}.

Trough out the analysis we mainly use three subsets of star particles, the
\emph{old stars} (age $>10$~Gyr, or GC candidates), the \emph{old insitu} stars
(defined as those bound to the most-massive halo/subhalo in the first snapshot
that the particle was recorded), and the \emph{old accreted} star particles
(i.e. those that have formed ex-situ and are bound to the most-massive halo/subhalo
at $z=0$). In addition, we include \emph{all stars} (no selection criterion) to
examine the result of (not) applying an age cut to our selection functions.

We consider the metallicity distribution in Sec.~\ref{sec:results_FeH}
the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
combination of both in Sec.~\ref{sec:results_FeHRgc}.

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in the Auriga
simulations is capable of i) producing a metallicity distribution that is
consistent with the GCS observed in the MW (M31), and ii) generating sufficient
mass over the domain of the observations.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        Mean and standard deviation of the metallicity distribution of star
        particles in each of the thirty Auriga L4 haloes. Orange dots show 
        the subset of old star particles, and blue (red) dots show the old 
        insitu (accreted) component. These Auriga subsets can be compared to 
        the MW (M31) GCS shown in purple (magenta), and to the metal-rich 
        (metal-poor) component of the MW GCS indicated by the black solid (open) 
        dots \citep[values from][p. 38]{1998gcs..book.....A}.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in all Auriga L4 simulations. The mean
metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
dispersion increases with decreasing metallicity. For comparison, the mean
of all star particles populates the range $-0.25$ to $0$ with a near-constant
dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than
the old- and old insitu populations. Most Auriga L4 haloes have old insitu
populations with mean metallicities around $-0.5$. The old accreted populations
follow the trent of increasing dispersion with decreasing mean metallicity, but
notably the old insitu populations all have a constant dispersion of roughly
$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
and literature values of the metal-rich (metal-poor) component of the MW GCS
as black solid (open) dots. We further discuss our comparison between the
simulations and the observations in Sec.~\ref{sec:discussion_FeH}

>>>>

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies. In theory, this information 
should be readily available and easily observable in the low redshift Universe, given 
that GCs survive nearly a Hubble time of evolution within the violent galactic 
environments they live in. However, these long and complex evolution histories
themselves imposes their imprints onto the GCs observables. Thus, a prerequisite to 
infer galactic histories from studies of GC systems is to understand the 
subtleties of the GC formation and evolution itself.

The literature offers several formation scenerarios that are consistent with the 
data. One important constraint comes from bimodality in the colour distribution, 
which is indicative of a bimodality in the underlying metallicity distribution 
of GC systems. For example, GCs in the MW are typically split up in a metal-rich 
(red) and metal-poor (blue) subpopulation divided at [Fe/H]~$=-1$ 
\citep[e.g.][]{Harris2001}. These two subpopulations could be associated to the 
galactic disk, respectively to the stellar halo \citep[e.g.][]{1985ApJ...293..424Z}. 
The latter is supported by observed similarities between the spatial distribution
and chemical signature of the `blue' GCs and the Galactic stellar halo 
\citep{2008A&ARv..15..145H}. Moreover, relative age-estimates indicate that the 
metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart 
\citep{2005AJ....130..116D}, providing futher support that the GC population indeed
consists of two distinct classes.

People postulate that the frequent mergers that occur during hierarchical build-up 
of galaxies naturally produce (sub)populations of GCs from enriched gas on tight 
orbits, if the mass ratios and gas fractions of the mergers are sufficiently high.

Boylan-Kolchin: the blue population could form in high density regions along the 
cosmic filament before or during the collapse of the proto-galaxy itself.
This formation scenario would explain the presence of the oldest GCs with 
primordial metallicities in the (outer) haloes of galaxies as the GCs are
accreted over time. Moreover, the tidal fields experienced by GCs at (outer) halo
orbits is significantly lower than by GCs in the inner galaxy, thus such GCs
are expected to be long-lived.

In a recent study, Chiou et al. speculate that GCs may form in supersonically
induced gasseous objects at high redshifts. These objects are free of dark matter 
and populate a mass range consistent with the typical mass scale of GCs. 
Interestingly, the authors find present-day absolute visual magnitude and 
characteristic scales consistent with GCs in the Local group, based on a 
rudimentary star formation model.

An alternative paradigm is that GC formation does not rely on special conditions
at high redshifts. Rather, the same physics that governs the formation of young 
massive clusters (YMCs) in the Local Group can be applied to the high redshift
Universe. The observed differences between YMCs and GCs, in this scenario, arise
naturally as the result intrinsic GC evolution within galactic tidal fields over
a Hubble time. This interesting hypothesis is tested numerically by the E-MOSAICS
people.

\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
formation.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (Figure~\ref{fig:MW-M31-age}),
and following the analysis of \citet{2017MNRAS.465.3622R}.

Trough out our analysis we compare the distributions of three subsets of star 
particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old insitu} 
stars (defined as those bound to the most-massive halo/subhalo in the first
snapshot that the particle was recorded), and \emph{old accreted} star particles 
(those that have formed ex-situ and are bound to the most-massive halo/subhalo
at $z=0$). For comparison we also include the results for \emph{all stars} (when
no additional selection criterion is applied to the star particles). We consider 
the metallicity distribution in Sec.~\ref{sec:results_FeH}, the distribution of 
galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW (M31) GC system, and whether 
the subgrid generates sufficient total mass to account for the bound cluster 
formation efficiency and evolutionary mass loss.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each dot represents one simulation for a given colour. The orange (blue) 
        [red] dots shows the values calculated using the old (old insitu) 
        [old accreted] star particles. Orange triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
of a given colour shows one particular simulation (thirty in total). The 
orange (blue) [red] dots represent the distributions of old (old insitu) 
[old accreted] star particles, and orange triangles indicate that all stars
were used. The mean metallicities of all GC candidates (orange dots) lie in the 
range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
distributions of the accreted (insitu) GC candidates shift to slightly lower 
(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
We find this trent that the distribution is more metal-poor (metal-rich)
when splitting the GC candidates into accreted (insitu) populations for the
majority of the Auriga simulations. The only exceptions are Au4-1 where this 
trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$

The purple (magenta) cross shows the values calculated using all MW (M31) GC
observations (i.e. assuming a unimodal distribution). The black solid (open) dots
mark the literature values of a bimodal Gaussian fit to the MW data, indicating
the metal-rich (metal-poor) subpopulation. Overall we find that the Auriga 
simulations produce (sub)populations of GC candidates that are more metal-rich 
than the MW and M31 GC systems. The only exception is Au4-1 with $\mu \approx -1.51$
and $\sigma \approx 0.54$, close to the mean of the blue/metal-poor population
of the MW GCS. However, the insitu GC candidates in Au4-1 consists 30 times
less star particles than any of the other (sub)population. Finally, we find that
the populations of GC candidates that have formed insitu have mean values that 
are similar the that of the red/metal-rich subpopulation of Milky Way GCs.

(sub)populations of GC candidates in the Auriga simulations has a metallicity
distribution with sufficiently low
